ms_borrador

### 2018-01-18 man/field_data.Rmd
update ms

---
title: "Field data work"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017"
output:  
  md_document:
    toc: true
    variant: markdown_github
bibliography: references.bib
csl: ecology.csl
---

>>>>

---
title: "Field data work"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017"
output:  
  md_document:
    toc: true
    variant: markdown_github
bibliography: ../refs/references.bib
csl: ../refs/ecology.csl
---

### 2018-01-18 man/ms_0_intro.Rmd
update methods
update ms

---
title: "ms_0_intro"
output:  
  md_document:
    toc: true
    variant: markdown_github
bibliography: ../references.bib
csl: ../ecology.csl
---

@@

>>>>

---
title: "ms_0_intro"
output:  
  md_document:
    toc: true
    variant: markdown_github
bibliography: ../refs/references.bib
csl: ../refs/ecology.csl
---

@@

`$NOTA$`: NDVI sirve para estimar la producción primaria neta. Existen diferentes estudio que han evaluado el efecto de la sequía sobre la producción primaria neta utilizando NDVI.

### 2018-01-18 man/ms_1_material_methods.Rmd
update methods
update ms

---
title: "material and methods"
output:  
  md_document:
    toc: true
    variant: markdown_github
bibliography: ../references.bib
csl: ../ecology.csl
---

@@

We tested for significant differences between drought events (2005 and 2012) and oak population (northern and southern slopes) for each of the resilience indices. Robust two-way ANOVAs were used beacuse original and log-transformed data both did not match the assumptions of normality and homogeneity of variance [@Wilcox2012]. Robust measures of central tendency (M-estimator based on Huber's Psi) were used since they were close to mean value in all cases [@Wilcox2012]. When running the robust ANOVA test, data were boostrapped 3000 times and trimmed automatically to control the potential influence of outliers [@Field2012; @Wilcox2012]. Post-hoc differences were assessed pairwise using a similar boostrap test. All the robust ANOVA and post-hoc tests were carried out using the `WRS2` [@Mair2017] and `rcompanion` [@Mangiafico2017] R packages. The level of significance was set at 0.05 and adjusted for multiple comparisons.

All analyses were carried out in R software [@R2017] and  using library dplR to standardize data, library nlme to fit the mixed models and vegan to run the PCA. All tests were at α = 0.05, except when indicated.

## References

>>>>

---
title: "material and methods"
output:  
  md_document:
    toc: true
    variant: markdown_github
bibliography: ../refs/references.bib
csl: ../refs/ecology.csl
---

@@

We tested for significant differences between drought events (2005 and 2012) and oak population (northern and southern slopes) for each of the resilience indices. Robust two-way ANOVAs were used beacuse original and log-transformed data both did not match the assumptions of normality and homogeneity of variance [@Wilcox2012]. Robust measures of central tendency (M-estimator based on Huber's Psi) were used since they were close to mean value in all cases [@Wilcox2012]. When running the robust ANOVA test, data were boostrapped 3000 times and trimmed automatically to control the potential influence of outliers [@Field2012; @Wilcox2012]. Post-hoc differences were assessed pairwise using a similar boostrap test. All the robust ANOVA and post-hoc tests were carried out using the `WRS2` [@Mair2017] and `rcompanion` [@Mangiafico2017] R packages. The level of significance was set at 0.05 and adjusted for multiple comparisons. All analyses were carried out in R software [@R2017] using several packages (see Supplementary S)

### 2018-01-18 man/ms_2_results.Rmd
UPDATE
update ms

---
title: "ms_2_results"
output:  
  md_document:
    toc: true
    variant: markdown_github
bibliography: ../references.bib
csl: ../ecology.csl
---

@@

Tree-growth exhibited a signigicant response to water availability more than to the temperatures. Cumulative precipitation of the hydrological year (September of the previous year to August of the growth year) influenced positively the tree-growth for the both northern and southern populations (FIG ). Precipitation of previous december was also positively correlated with tree growth in the northern population and in the highest location of the southern population. Hydrological, Spring and Summer SPEI showed a strong positive correlation with tree-growth, specially for northern population. Spring Maximum temperature was the most significant limitation of the tree-growth for the southern population while maximum temperatures of the previous August did for the northern one. Conversely, mean, minimum and maximum temperatures of current September positively influenced the tree-growth in the northern population.

>>>>

---
title: "ms_2_results"
output:  
  md_document:
    toc: true
    variant: markdown_github
bibliography: ../refs/references.bib
csl: ../refs/ecology.csl
---

@@

Tree-growth exhibited a significant response to water availability more than to the temperatures. Cumulative precipitation of the hydrological year (September of the previous year to August of the growth year) influenced positively the tree-growth for the both northern and southern populations (FIG ). Precipitation of previous december was also positively correlated with tree growth in the northern population and in the highest location of the southern population. Hydrological, Spring and Summer SPEI showed a strong positive correlation with tree-growth, specially for northern population. Spring Maximum temperature was the most significant limitation of the tree-growth for the southern population while maximum temperatures of the previous August did for the northern one. Conversely, mean, minimum and maximum temperatures of current September positively influenced the tree-growth in the northern population.

### 2018-01-18 man/ms_figures.Rmd
update
update ms

---
title: "ms_figures"
output:  
  md_document:
    toc: true
    variant: markdown_github
bibliography: ../references.bib
csl: ../ecology.csl
---

@@

>>>>

---
title: "ms_figures"
output:  
  md_document:
    toc: true
    variant: markdown_github
bibliography: ../refs/references.bib
csl: ../refs/ecology.csl
---

@@

### Figure 1

![](../out/fig/geomap/mapa_situacion.jpg)

### 2018-01-18 man/ms_tables_portrait.Rmd
update ms

---
title: "ms_tables_portrait"
output:
  word_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 7.5
    highlight: null
    reference_docx: template_tables_portrait.docx
bibliography: ../references.bib
csl: ../ecology.csl
---

>>>>

---
title: "ms_tables_portrait"
output:
  word_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 7.5
    highlight: null
    reference_docx: template_tables_portrait.docx
bibliography: ../refs/references.bib
csl: ../refs/ecology.csl
---

### 2018-01-18 man/notes_EVI.Rmd
add notas sobre EVI
update ms

---
title: "notes EVI"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017 nov"
output:  
  md_document:
    toc: true
    variant: markdown_github
bibliography: ../references.bib
csl: ../ecology.csl
---

@@

>>>>

---
title: "notes EVI"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017 nov"
output:  
  md_document:
    toc: true
    variant: markdown_github
bibliography: ../refs/references.bib
csl: ../refs/ecology.csl
---

@@

# Filtrado de datos

Para el filtrado de datos ver el siguiente link
[`./analysis/prepare_modis_qa.md`](/analysis/prepare_modis_qa.md)

### 2018-01-18 man/notes_competition_index.Rmd
update ms

---
title: "Competition notes"
author: "AJ Perez-Luque (@ajpelu)"
date: "2016 Dic"
output:  
  md_document:
    toc: true
    variant: markdown_github
bibliography: ../references.bib
csl: ../ecology.csl
---

>>>>

---
title: "Competition notes"
author: "AJ Perez-Luque (@ajpelu)"
date: "2016 Dic"
output:  
  md_document:
    toc: true
    variant: markdown_github
bibliography: ../refs/references.bib
csl: ../refs/ecology.csl
---

### 2018-01-18 man/notes_dendro.Rmd
update ms

---
title: "Dendrocronology notes"
author: "AJ Perez-Luque (@ajpelu)"
date: "2016 Nov"
output:  
  md_document:
    toc: true
    variant: markdown_github
bibliography: ../references.bib
csl: ../ecology.csl
---

>>>>

---
title: "Dendrocronology notes"
author: "AJ Perez-Luque (@ajpelu)"
date: "2016 Nov"
output:  
  md_document:
    toc: true
    variant: markdown_github
bibliography: ../refs/references.bib
csl: ../refs/ecology.csl
---

### 2018-01-18 man/report.Rmd
update ms r
add template
include tables rmd child
add figures
updating
update ms

---
title: "ms_borrador"
author: "AJ Perez-Luque; G. Gea-Izquierdo; R. Zamora; FJ. Bonet"
date: "2017"
output:  word_document
bibliography: ../references.bib
csl: ../ecology.csl
---

@@

>>>>

---
title: "ms_borrador"
author: "AJ Perez-Luque; G. Gea-Izquierdo; R. Zamora; FJ. Bonet"
date: "2017"
output:
  word_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 7.5
    highlight: null
    reference_docx: template_ms.docx
bibliography: ../refs/references.bib
csl: ../refs/ecology.csl
---

@@

```{r child = 'ms_3_discussion.Rmd'}
```

```{r child = 'ms_tables.Rmd'}
```

```{r child = 'ms_figures.Rmd'}
```
